\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-18 doc/sw-system.tex
Closed #136 with short note on project renaming

A screenshot of the \SW classification interface (CI) is shown in
\Fref{fig:screenshot}. The CI is the centrepiece of the \SW website,
\texttt{http://spacewarps.org}; the web application is written in coffeescript,
css and html and follows the general design of others written by the Zooniverse
team.\footnote{The \SW web application code is open source and can be accessed
from \texttt{https://github.com/zooniverse/Lens-Zoo}}  The focus of the CI is a
large display of a pre-prepared PNG image of the ``subject'' being inspected.
When the image is clicked on by the volunteer, a marker symbol appears where the
pointer was. Several markers can be placed.

>>>>

A screenshot of the \SW classification interface (CI) is shown in
\Fref{fig:screenshot}. The CI is the centrepiece of the \SW website,
\texttt{http://spacewarps.org}; the web application is written in coffeescript,
css and html and follows the general design of others written by the Zooniverse
team.\footnote{The \SW web application code is open source and can be accessed
from \texttt{https://github.com/zooniverse/Lens-Zoo}. The project was renamed during development.}
The focus of the CI is a
large display of a pre-prepared PNG image of the ``subject'' being inspected.
When the image is clicked on by the volunteer, a marker symbol appears where the
pointer was. Several markers can be placed.
